Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-25 paper.tex
all fits in 4 pages - really this time!

Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
         & Storage    & Residence Time            \\
\toprule
CyCLASS  & Reactor    & Cycle Length              \\\cmidrule{3-3}
         &            & Power                     \\\cmidrule{3-3}
         &            & Fuel Enrichment (\gls{LWR}-\gls{UOX} \\

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition.  While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities (parameters randomly generated at each new facility deployment).
This kind of study will to be extended to random uncertainty (new parameter
values as a function of time) and completely systematic uncertainty (shared by all
the facilities of a kind).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \appendix
%% \section{Appendix}
%%
%% Numbering in the appendix is different:
%% \begin{equation} \label{eq:appendix}
%%   2 + 2 = 5\,.
%% \end{equation}
%% and another equation:
%% \begin{equation} \label{eq:appendix2}
%%   a + b = c\,.
%% \end{equation}
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \section{Nomenclature}
%%
%% \begin{table}[H]
%%     \centering
%%     \begin{tabular}{l|l}
%% %         &  \\
%%         $N$ & Feed assay \\
%%         $N'$ & Product assay \\
%%         $N''$ & Tails assay \\
%%         $\alpha$ & Feed to product enrichment factor \\
%%         $\beta$ & Feed to tail enrichment factor \\
%%         $\theta$ & Cut
%%     \end{tabular}
%% %    \caption{Caption}
%%     \label{tab:my_label}
%% \end{table}

%% \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
%%   \centering
%%   \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
%%   \caption{Illustration of the material flow between the different level of
%%       cascades without tail recycling, in this diagram, nu\_src corresponds to
%%       an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
%%       $\{n\}$ to the cascade and the storage getting the products of the
%%       cascades at the level $\{n\}$.}\label{fig:flow}
%% \end{figure}

%% \begin{table}[htb]
%% \centering
%%   \caption{Summary of cascade properties for each level.}
%% \begin{tabular}{cllll}
%% \toprule
%%
%% Level   &           & Assay     &       & Machines  \\
%%         & Feed      & Product   & Feed  &           \\
%% \midrule
%% 0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
%% 1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
%% 2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
%% 3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
%% 4       & 0.8834    & 0.9735    & 0.7746 & 169       \\
%%
%% \bottomrule
%% \end{tabular}
%%
%%   \label{tab:cascadelvl}
%% \end{table}

>>>>

Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
         & Storage    & Residence Time            \\
\toprule
CyCLASS  & Reactor    & Cycle Length              \\\cmidrule{3-3}
         &            & Power                     \\\cmidrule{3-3}
         &            & \acrshort{LWR}-\acrshort{UOX} Fuel Enrichment\\

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition.  While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities.
This kind of study will to be extended to random uncertainty (new parameter
values as a function of time) and completely systematic uncertainty (shared by all
the facilities of a kind).

@@
